\Large \bf \Toolname: Cache Line Contention Detection for COTS Binaries

### 2014-12-13 HotOS'15/paper.tex
Working on related work section. Re-did most of the intro. No abstract yet.

% For leaving some comments in the draft.
\newcommand{\comment}[1]{}
\newcommand{\Toolname}{DataReactor}

@@

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf \Toolname: Precise False Sharing Detection for COTS Binaries}
\numberofauthors{3}
\author{
% 1st. author
\alignauthor
Peter Goodman\\
       \email{pag@cs.toronto.edu}
\and
% 2nd. author
\alignauthor
Ashvin Goel\\
       \email{asvhin@eecg.toronto.edu}
% 3rd. author
\alignauthor
Angela Demke Brown\\
       \email{demke@cs.toronto.edu}
}
\maketitle

@@

% Key ideas:
%		1) 	Shadow memory as a proxy for memory accesses, not as a meta-data store.
%		2) 	Tagged reads as a way to avoid cache contention on shadow memory, but still
%			highlight the essential memory access behaviour.
%		3)	Proportional heap sampling, by using type-specific information to decide where
%			to place hardware watchpoints.

False-sharing is a performance-degrading problem that limits the scalability of multithreaded applications
\cite{ImpactOfFalseSharing}. This problem is increasingly important in the multi-core era. The level of
concurrency in applications is growing to match the additional processing power provided by increasing
core counts on modern processors. Despite this rise in importance, detecting and diagnosing false
sharing in large systems remains challenging. Due to the nature of cache coherent multiprocessors, false
sharing is often indistinguishable from true sharing (including data races). Also, diagnosing the cause
of false sharing requires that one distinguish accesses to the same objects from ``pseudo sharing", which
occurs when two nearby objects are separately but concurrently accessed \cite{DegenerateSharingAndFalseCoherence}.

In this work, we present \Toolname{}, a system for precisely detecting and diagnosing false sharing
in multi-threaded applications. \Toolname{} uses dynamic binary translation (DBT) and shadow memory
to detect false sharing in commercial off-the-shelf (COTS) binaries.  The key insight of our
approach is that accesses to shadow memory can be used as a proxy for accesses to actual memory. By 
detecting contention on proxied accesses, we can establish beliefs about what code causes false sharing. These
beliefs are strenghtened and eventually verified by specializing code to proxy memory accesses at increasingly
finer granularities.

Our work addresses three limitations of prior work:
\begin{enumerate}
\item They introduce extra cache coherency traffic, which limits scalability and hides performance
problems. The extra traffic introduced comes from the mechanisms used to track cache line ownership.

\item They are unable to selectively detect false sharing on only specific types of objects or specific
code.

\item They are imprecise: they cannot distinguish between false sharing, true sharing (including
data races), and and pseudo sharing. This can result in high false-positive rates that decrease the
usefulness of the tools.

@@

\paragraph{Contributions}
This paper makes the following significant contributions:
\begin{itemize}
\item It presents \Toolname{}, a software-only framework that dynamically and precisely diagnoses
false sharing  in multi-threaded, COTS binaries. We believe that operating directly on binaries is
important because it allows one to verify observed performance problems using the same binaries
that are running in a production environment.

\item It presents two new techniques, \emph{proxy memory} and \emph{tagged reads}, that enable
efficient determination of memory access behavior using shadow memory. Unlike existing shadow
memory systems, proxy memory is not treated as a mutable meta-data store. This avoids extra
serialization and coherence traffic introduced by prior work when dynamically manipulating shadow state.

\item It describes two new, data-centric sampling approaches: uniform heap sampling, and selective heap
sampling. Uniform heap sampling enables \Toolname{} to sample objects in the heap uniformly according to
their type. This is beneficial because it improves coverage: if 90\% of false sharing occurs because of accesses
to only 10\% of the data, then \Toolname{} will not miss those races by blindly focusing on the other 90\% of data.
Once data of interesting has been narrowed down, \Toolname{} can apply selective heap sampling, which
focuses sampling on specific types of objects or data accessed by specific code (or both).
\end{itemize}

@@

\section{Related Work}\label{sec:background}
\Toolname{} primarily draws on techniques from existing race detectors and false sharing detectors.
This is appropriate because some forms of false-positives for race detectors are caused by false
sharing. That is, where race detectors focus on two threads concurrently accessing the same
data, false sharing detectors focus on two threads concurrently accessing different data, but
on the same cache line.

% --------------------------------------
\subsection{Race Detection}

Race detectors can be categorized according to the following parameters:
\begin{description}
\item[Approach] Static or dynamic. \hfill \\
Static race detectors analyze source code or binaries, typically performing interprocedural control-
and data-flow analyses. The benefit of static analysis is that they can inspect all program paths.

Dynamic race detectors monitor memory accesses for races. The benefit of this approach is that
races can be caught "in the act". The drawbacks of this approach is that most dynamic race detectors
are too slow to run in production environments, and therefore must be tested on simulated workloads.
If these workloads do not exercise all code paths than many races can be missed. Dynamic race detectors
can be further broken down into on-the-fly detectors or post-mortem detectors, which analyze memory
access logs.

\item[Model] Precise or imprecise.  \hfill \\
Precise race detectors report no false-positives and are usually implemented using Lamport's
happens-before relationship \cite{VectorClocks}. Precise race detectors often trade efficiency
for completeness in order to achieve their precision. That is, they sometime miss true races in
code.

Imprecise race detectors can have high false positive rates, but tend to be more complete in terms of
including races not detected by precise detectors. They tend to be implemented using a variant of the
lockset algorithm \cite{Eraser}.

\item[Granularity] Fine-grained or coarse-grained. \hfill \\
Fine-grained race detectors operate at or close to the granularity of memory accesses. Coarse-grained
race detectors operate at an object granularity, or at a fixed granularity (e.g. cache line, page).

The granularity of a race detector can affect its precision. For example, a happens-before race detector 
can be imprecise (i.e. report false positives) by operating at a coarse granularity. If the granularity were
the size of a cache line, then the race detector would be a cache line contention detector: it would hint
at races as well as false-sharing.

\item[Mode] Comprehensive or sampling-based. \hfill \\
Comprehensive race detectors typically analyze every memory read and write. They are usually implemented
by instrumenting all program code.

Sampling-based race detectors analyze either a subset of the code or a subset of the data. In the former
case, they focus on detecting races by specific code.
\end{description}

Under this categorization scheme, \Toolname{} is a dynamic, precise, variable-granularity, mixed-mode
false-sharing detector. It draws inspiration from a number of existing race detectors, including LiteRace
\cite{LiteRace}, MultiRace \cite{MultiRace}, RaceMob \cite{RaceMob}, RaceTrack \cite{RaceTrack}, and
DataCollider \cite{DataCollider}.

@@

DataCollider \cite{DataCollider} is a dynamic, precise, sampling-based race detector for the kernel. The key strengths of
DataCollider is that it has low overhead, it is independent of the synchronization mechanisms being employed, and that
it often catches both threads in the act. DataCollider uniformly samples code by introducing breakpoints into the code.
When a breakpoint is hit, a hardware watchpoint is added to data that was about to be accessed by the interrupted instruction.
Then, the interrupted thread is paused for a short period of time to give another thread the opportunity to access the
same data, thus triggering the watchpoint and detecting a race. This brilliantly simple approach was the main inspiration
for \Toolname{}. \Toolname{} differs from DataCollider, in that the latter is code-centric insofar as it samples code, whereas
\Toolname{} is data-centric insofar as it samples data.

% --------------------------------------
\subsection{False Sharing Detection}

Similar to race detectors, false-sharing detectors can be sampling-based or comprehensive. Comprehensive approaches
can be categorized  into simulation-based and instrumentation-based approaches. Simulation-based approaches focus on
simulating the full cache hierarchy and can distinguish fine-grained events like false sharing due to set-associativity and
false sharing due to different data being accessed on the same cache line. Instrumentation-based approaches focus more
on mechanisms for estimating or detecting cache line contention.

\paragraph{Sampling-based}
Intel's VTune \cite{IntelVTune} an an imprecise, sampling-based profiler that can detect false sharing using hardware performance
counters and monitoring events. It represents the state-of-the-art in performance analysis tools and is able to provide detailed,
architecture-specific performance-tuning suggestions. Unlike \Toolname{}, VTune is unable to analyze only a portion of the code,
or only the portion of code that accesses specific shared data structures.

\paragraph{Comprehensive}

@@

\newcommand{\DrContention}{Zhao \emph{et al.}}

\DrContention{} \cite{DrContention} implement a dynamic false and true sharing detector using the DynamoRIO \cite{DynamoRIO}
DBT system and Umbra shadow memory framework \cite{Umbra}. Unlike \Toolname{}, \DrContention{} use fixed-granularity
shadow memory to track cache line ownership by processor cores. The drawback of this approach is that it necessitates checking
and updating the shadow memory on every memory access, which introduces its own form of cache line contention. \Toolname{}
avoids this issue by using shadow memory and tagged reads as a proxy for memory access behavior instead of as a meta-data store.

Plastic \cite{Plastic} is a Xen-based dynamic false sharing detector and repairer. Like \Toolname{}, it takes a pipeline-based
approach that successively narrows down on the root causes of false sharing. Plastic also uses DBT as part of its
repair mechanism. Plastic's pipeline begins by using hardware performance counters related to cache contention
events to detect the presence of false-sharing. Then, it applies a similar technique to MultiRace \cite{MultiRace}, in
that it tracks the dominant access pattern by each thread to memory on a shared page. This information informs
their repair mechanism, which transparently re-maps memory accesses at a byte granularity.

SHERIFF \cite{SHERIFF} is a false-sharing detector and repairer that works in a similar way to MultiRace and Plastic. Initially,
it applies read-only hardware page protection to all shared memory. Then, as threads attempt to write to protected pages, those
pages are privately mapped as read/write. When the same page is privately mapped by two or more threads, SHERIFF applies
the twinning and diffing approach of TreadMarks \cite{TreadMarks} to detect local changes to shared pages and narrow down
on instances of false sharing. Like \Toolname{}, SHERIFF uses a coarse-grained mechanism to hint at the potential for races.

>>>>

% For leaving some comments in the draft.
\newcommand{\comment}[1]{}
\newcommand{\TextToolname}{CatcheScan}
\newcommand{\Toolname}{\textsc{\TextToolname{}}}
\newcommand{\BoldToolname}{\textsc{\bf\TextToolname{}}}

@@

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf \Toolname: Cache Line Contention Detection for COTS Binaries}
\numberofauthors{3}
\author{
% 1st. author
\alignauthor
Peter Goodman\\
       \email{pag@cs.toronto.edu}
\and
% 2nd. author
\alignauthor
Ashvin Goel\\
       \email{asvhin@eecg.toronto.edu}
% 3rd. author
\alignauthor
Angela Demke Brown\\
       \email{demke@cs.toronto.edu}
}
\maketitle

@@

In multi-threaded applications, cache-line contention is a symptom of several kinds of bugs: data races, true sharing,
false sharing, and pseudo sharing. Data races are potential correctness bugs that introduce non-determinism into running
programs. True, false, and pseudo sharing are performance bugs that limit the scalability of multi-threaded applications
\cite{ImpactOfFalseSharing}. Both problems are important in the multi-core era, where the level of concurrency in
applications is growing to match the additional processing power provided by increasing core counts on modern processors.

% Despite this rise in importance, detecting and diagnosing false
%sharing in large systems remains challenging. Due to the nature of cache coherent multiprocessors, false
%sharing is often indistinguishable from true sharing (including data races). Also, diagnosing the cause
%of false sharing requires that one distinguish accesses to the same objects from ``pseudo sharing", which
%occurs when two nearby objects are separately but concurrently accessed \cite{DegenerateSharingAndFalseCoherence}.

This paper presents \BoldToolname{}, a software-only runtime for precisely detecting and diagnosting cache line
contention in commercial, off-the-shelf (COTS) x86-64 program binaries. \Toolname{} addresses three limitations of prior
work: \begin{enumerate}
\item They are not general: they require an understanding of the semantics of all synchronization primitives used
by the program. This is unsatisfactory for COTS binaries that employ lock-free algorithms and home-grown synchronization
primitives.

\item They are imprecise: they cannot distinguish between data races, true sharing, false sharing, and pseudo sharing
\cite{DegenerateSharingAndFalseCoherence}. This can result in high false-positive rates or confusing reports that decrease
the usefulness of these tools for practitioners.

\item They are not comprehensive: they miss actual cases of cache line contention because they use heuristics to sample 
or instrument only a subset of the code, and therefore lose visibility on accesses to data that might cause bugs.

%\item They are not selective. While apparently at odds with comprehensiveness, they track or instrument \emph{too much}, 
%and therefore waste time looking for problems where none exist.

%\item They introduce extra cache coherency traffic, which limits scalability and hides performance
%problems. The extra traffic introduced comes from the mechanisms used to track cache line ownership.

%\item They are unable to selectively detect false sharing on only specific types of objects or specific
%code.

@@

\Toolname{} uses dynamic binary translation (DBT) to instrument a program binary and detect cache line contention
at runtime. Our approach combines unlimited watchpoints \cite{UnlimitedWatchpoints,DynamoRIOWatchpoints}, data
sampling, and a lightweight cache line ownership tracking mechanism to detect cache line contention. The key insight
of our approach is that if we know \begin{inparaenum}[i)]
\item what code is executed by more than one thread,
\item what types of data are accessed by more than one thread, and
\item what types of data are accessed by what code, then
\end{inparaenum}
we can efficiently detect cache line contention by selectively instrumenting only the code and the data that matters.

%we can extend on and improve existing techniques to detecting
%cache line contention by combining solutions the following problems:
%\begin{enumerate}
%\item Code concurrency: Detecting what code is executed by more than one thread.
%\item Data concurrency: Detecting what types of data are accessed by more than one thread.
%\item Code polymorphism: Detecting what code accesses what types of data.
%\end{enumerate}

% infinite software watchpoints, as implemented within a DBT system, as
%well as being selective about what parts of the program to

%The key insight of our
%approach is that accesses to shadow memory can be used as a proxy for accesses to actual memory. By 
%detecting contention on proxied accesses, we can establish beliefs about what code causes false sharing. These
%beliefs are strenghtened and eventually verified by specializing code to proxy memory accesses at increasingly
%finer granularities.

\paragraph{Contributions}
This paper makes the following significant contributions:
\begin{itemize}
\item It describes \Toolname{}, a software-only system that dynamically and precisely diagnoses cache line
contention in multi-threaded, COTS binaries. This enables \Toolname{} to detect performance
and correctness bugs in programs using home-grown synchronization primitives and lock-free algorithms.

\item It describes a new data-centric sampling approach, \emph{comprehensive data sampling}, that improves
sampling coverage and contention detection accuracy. Comprehensive sampling uniformly samples objects in
memory  according to their type. This avoids problems related to sampling bias in situations where a
relatively small amount of shared data is crowded out by a much larger amount of unshared data (as happens
when multi-threaded programs operate on partitions of a data set).

%from wasting cycles looking for contention on
%unshared data

%This is beneficial because it improves coverage: if 90\% of false sharing occurs because of accesses
%to only 10\% of the data, then \Toolname{} will not miss those races by blindly focusing on the other 90\% of data

\item It describes a novel separation of cache line contention detection into two phases: \begin{enumerate}
\item[1) \emph{Training:}] an ahead-of-time, heavyweight analysis of the program's execution that
discovers what code can contain cache line contention, and what data is shared by multiple threads. A key
aspect of this phase is that it \emph{does not} need to exhibit any cache line contention; the only requirement
is that training and production workloads exercise/cover the code in similar ways.

% TODO: Evaluate by showing the percentage of code that doesn't get instrumented at all, or is only
% instrumented with lightweight instrumentation.

\item[2) \emph{Detection:}] an online analysis that detects cache line contention by selectively
instrumenting only the relevant code and sampling only the relevant data as recognized by the
offline training phase.
\end{enumerate}

This separation is motivated by the need to reduce instrumentation overheads of the detection phase by
as much as possible in order to maximize the detection accuracy (e.g. data races are time-sensitive). The key
insight enabling this separation is that time--and therefore the cost of instrumentation--does not matter to
the accuracy of the results produced by the training phase.

%A key aspect of the training phase is that it must exhibit approximately the same code coverage as a
%production
%that it does not need to exhibit a buggy execution (i.e. contain actual
%cache line contention)

%It describes a novel separation of cache line contention detection into two phases: \begin{enumerate}
%\item[1) \emph{Training:}] This phase uses heavyweight instrumentation to discover \begin{inparaenum}
%\item what code is hot;
%\item what code is executed by more than one thread;
%\item what code accesses what data; and,
%\item function call graphs.
%\end{inparaenum}
%
%This information enables the detection phase to selectively prune the set of code that is instrumented,
%and the set of data that is sampled in order to reduce overheads. 
%
%
%
%\item[2) \emph{Detection:}] b
%\end{enumerate}

%ahead-of-time training phase that discovers code and data that can be ignored
%during online analysis, thus reducing online instrumentation overheads. The key insight is that all training
%data gathered is 
%time--and
%time spent--doing offline analysis does not affect the accuracy of the results produced. This is important
%because discovering what code can be pruned and what data does

%\begin{enumerate}
%\item Detecting what code is important to the 
%\end{enumerate}
%
%analyzing
%the 
%
%the detection
%of what code should be instrumented and what data should be sampled is \emph{not} time-sensitive, and
%therefore can be performed any time. 
%
%using results gathered from
%an offline learning and analysis phase. This separation is motivated by recognizing that

%\item It presents two new techniques, \emph{proxy memory} and \emph{tagged reads}, that enable
%efficient determination of memory access behavior using shadow memory. Unlike existing shadow
%memory systems, proxy memory is not treated as a mutable meta-data store. This avoids extra
%serialization and coherence traffic introduced by prior work when dynamically manipulating shadow state.

%\item It describes two new, data-centric sampling approaches: uniform heap sampling, and selective heap
%sampling. .
%Once data of interesting has been narrowed down, \Toolname{} can apply selective heap sampling, which
%focuses sampling on specific types of objects or data accessed by specific code (or both).
\end{itemize}

@@

\section{Overview}\label{sec:overview}

\Toolname{} uses DBT to instrument the memory accesses of a program while it is running. During the offline
learning phase, DBT is used to figure out what code is executed by more than one thread, what data is accessed
by more than one thread, and what code accesses what data. During its online detection phase, \Toolname{} uses
an implementation of unlimited watchpoints watch for accesses to a representative sample of cache lines, assign
owning threads to those cache lines, and finally detect transfers in ownership.

\subsection{Definitions}
\Toolname{} looks for cache line contention bugs of the following forms:
\begin{description}
\item[Data races] Data races occur when the same program variable is concurrently modified by two threads, or 
modified by one thread and concurrently accessed by another thread, where neither access is atomic (e.g. using
and atomic read-modify-write instruction).

\item[True sharing] True sharing has the same access pattern as a data race, except that one or both operations
are atomic.

\item[False sharing] False sharing occurs when two semantically related variables (e.g. two fields in a struct) occupy
the same cache line and are concurrently accessed, thus introducing contention on the cache line.

\item[Pseudo sharing] Pseudo sharing occurs when two semantically unrelated variables (e.g. fields in adjacent structs,
adjacent array entries) occupy the same cache line and are concurrently accessed \cite{DegenerateSharingAndFalseCoherence}.
\end{description}

%\subsection{Mechanisms}

\section{Related Work}\label{sec:background}
\Toolname{} draws on and extends/refines techniques from existing race detectors and false sharing detectors.

%% --------------------------------------
\paragraph{Dr. Memory}
Dr. Memory \cite{DrContention} implements a set of tools for detecting cache line contention, thread correlations,
and true/false sharing detection in COTS binary programs. Dr. Memory uses the DynamoRIO \cite{DynamoRIO} DBT system
and the Umbra shadow memory framework \cite{Umbra} to interpose on memory accesses and implement their
detection tools. Dr. Memory's contention tool implements the following algorithm for detecting contention. Before each
memory write,  instrumentation performs a ``racy" check to see if the current thread owns the cache line being accessed.
If the cache line is owned by another thread, then a report is generated, and ownership is transferred. If the cache line is
unowned, then ownership is established.

This approach has two drawbacks. First, every time ownership is transferred/established, there is an additional
memory write, which itself introduces CPU overheads due to contention on the cache lines of the shadow memory. Second,
ownership is tracked on data that is never shared. This introduces extra CPU and memory overheads by instrumenting
too much code and tracking too much data.

\Toolname{} addresses both problems. First, its offline learning phase prunes the set of code that should be instrumented.
This has the side effect of reducing the physical memory requirements of shadow memory because fewer instructions will
introduce shadow accesses, and therefore less shadow is accessed. Second, our sampling approach means that ownership
is only tracked for ``watched" objects. This introduces an additional racy read at the beginning of instrumentation, but the
benefit is that the majority of shadow accesses are read-only, and therefore do not generate as much additional contention
on the cache lines associated with shadow memory.

%% --------------------------------------
\paragraph{DataCollider}
DataCollider \cite{DataCollider} is a precise, sampling-based race detector for the WIndows kernel. DataCollider's key
novelties are its extremely low overhead, as well as its generality: it detects data races without any understanding of
a system's underlying synchronization primitives. DataCollider uniformly samples code by introducing breakpoints into the code.
When a breakpoint is hit, a hardware watchpoint is added to data that was about to be accessed by the interrupted instruction.
Then, the interrupted thread is paused for a short period of time to give another thread the opportunity to access the
same data. If the data is accessed by a second thread while the first thread is paused, then the watchpoint will detect the
access, thus allowing DataCollider to detect a race ``in the act.""

While this approach is elegant in its simplicity, it has two major drawbacks. First, its dependence on hardware watchpoints
limits it to being able to detect races on at most four distinct 8-byte memory locations simultaneously \cite{IntelSDManual}.
Second, it cannot detect guarded cache line line conflicts: if the same cache line is concurrently accessed by two threads, but
the accesses are guarded by a lock, then the pausing introduced by the first thread will prevent the watchpoint from being hit
in the second thread (because the second thread will block on the lock).

%% --------------------------------------
\paragraph{Other}

Intel's VTune \cite{IntelVTune} an an imprecise, sampling-based profiler that can detect false sharing using hardware performance
counters and monitoring events. It provides detailed, architecture-specific performance-tuning suggestions. Unlike \Toolname{},
VTune can only report individual program counters that general cache coherency events, but cannot correlate threads by showing
two contending stack traces.

%, thus triggering the watchpoint and detecting a race ``in the act".
%
%%sampling based approach enables it to be general
%
% The key strengths of
%DataCollider is that it has low overhead, it is independent of the synchronization mechanisms being employed, and that
%it often catches both threads in the act.  This brilliantly simple approach was the main inspiration
%for \Toolname{}. \Toolname{} differs from DataCollider, in that the latter is code-centric insofar as it samples code, whereas
%\Toolname{} is data-centric insofar as it samples data.

%In either case, a memory write occurs to take ownership.

%\DrContention{} comprehensively interposes on
%all memory accesses to track ownership of all cache lines. Every instruction is instrumented to first check if the current
%thread owns the cache line. If not, then the thread is added to the cache line's \emph{threadset}.

% TODO: Evaluate by disabling is_watched check, i.e. perform ownership tracking on all cache lines, vs. only a subset
% of cache lines.

%Several tracking mechanisms are discussed, including ones that
%track strict ownership transers, and others that attempt to measure thread correlations and the impact of of cache line
%invalidations. The drawback of this approach is that it necessitates checking and updating the shadow memory on every
%memory access, which introduces performance overhead due to extra cache line contention.

%Like \DrContention{}, \Toolname{} uses DBT and shadow memory to track ownership of cache lines. However, \Toolname{}
%only tracks cache line ownership for a subset of the cache lines (those currently being sampled). This makes a big difference
%because, although potentiall all instructions are instrumented for shadow memory, only a small subset of th

\paragraph{Plastic}
Plastic \cite{Plastic} is a Xen-based dynamic false sharing detector and repairer. Like \Toolname{}, it takes a pipeline-based
approach that successively narrows down on the root causes of false sharing. Plastic also uses DBT as part of its
repair mechanism. Plastic's pipeline begins by using hardware performance counters related to cache contention
events to detect the presence of false-sharing. Then, it applies a similar technique to MultiRace \cite{MultiRace}, in
that it tracks the dominant access pattern by each thread to memory on a shared page. This information informs
their repair mechanism, which transparently re-maps memory accesses at a byte granularity.

\paragraph{SHERIFF}
SHERIFF \cite{SHERIFF} is a false-sharing detector and repairer that works in a similar way to MultiRace and Plastic. Initially,
it applies read-only hardware page protection to all shared memory. Then, as threads attempt to write to protected pages, those
pages are privately mapped as read/write. When the same page is privately mapped by two or more threads, SHERIFF applies
the twinning and diffing approach of TreadMarks \cite{TreadMarks} to detect local changes to shared pages and narrow down
on instances of false sharing. Like \Toolname{}, SHERIFF uses a coarse-grained mechanism to hint at the potential for races.

%% --------------------------------------
%\subsection{Race Detection}
%
%Race detectors can be categorized according to the following parameters:
%\begin{description}
%\item[Approach] Static or dynamic. \hfill \\
%Static race detectors analyze source code or binaries, typically performing interprocedural control-
%and data-flow analyses. The benefit of static analysis is that they can inspect all program paths.
%
%Dynamic race detectors monitor memory accesses for races. The benefit of this approach is that
%races can be caught "in the act". The drawbacks of this approach is that most dynamic race detectors
%are too slow to run in production environments, and therefore must be tested on simulated workloads.
%If these workloads do not exercise all code paths than many races can be missed. Dynamic race detectors
%can be further broken down into on-the-fly detectors or post-mortem detectors, which analyze memory
%access logs.
%
%\item[Model] Precise or imprecise.  \hfill \\
%Precise race detectors report no false-positives and are usually implemented using Lamport's
%happens-before relationship \cite{VectorClocks}. Precise race detectors often trade efficiency
%for completeness in order to achieve their precision. That is, they sometime miss true races in
%code.
%
%Imprecise race detectors can have high false positive rates, but tend to be more complete in terms of
%including races not detected by precise detectors. They tend to be implemented using a variant of the
%lockset algorithm \cite{Eraser}.
%
%\item[Granularity] Fine-grained or coarse-grained. \hfill \\
%Fine-grained race detectors operate at or close to the granularity of memory accesses. Coarse-grained
%race detectors operate at an object granularity, or at a fixed granularity (e.g. cache line, page).
%
%The granularity of a race detector can affect its precision. For example, a happens-before race detector 
%can be imprecise (i.e. report false positives) by operating at a coarse granularity. If the granularity were
%the size of a cache line, then the race detector would be a cache line contention detector: it would hint
%at races as well as false-sharing.
%
%\item[Mode] Comprehensive or sampling-based. \hfill \\
%Comprehensive race detectors typically analyze every memory read and write. They are usually implemented
%by instrumenting all program code.
%
%Sampling-based race detectors analyze either a subset of the code or a subset of the data. In the former
%case, they focus on detecting races by specific code.
%\end{description}

%Under this categorization scheme, \Toolname{} is a dynamic, precise, variable-granularity, mixed-mode
%false-sharing detector. It draws inspiration from a number of existing race detectors, including LiteRace
%\cite{LiteRace}, MultiRace \cite{MultiRace}, RaceMob \cite{RaceMob}, RaceTrack \cite{RaceTrack}, and
%DataCollider \cite{DataCollider}.

@@

%% --------------------------------------
%\subsection{False Sharing Detection}
%
%Similar to race detectors, false-sharing detectors can be sampling-based or comprehensive. Comprehensive approaches
%can be categorized  into simulation-based and instrumentation-based approaches. Simulation-based approaches focus on
%simulating the full cache hierarchy and can distinguish fine-grained events like false sharing due to set-associativity and
%false sharing due to different data being accessed on the same cache line. Instrumentation-based approaches focus more
%on mechanisms for estimating or detecting cache line contention.

%\paragraph{Sampling-based}

%\paragraph{Comprehensive}

@@
